Balance responses in MS

### 2020-01-28 R/msBalance.Rmd
first interpolation of EMG data

# if csv files do not exist, run matlab batch steps
if (!file.exists("../csv/c.csv")|!file.exists("../csv/m.csv")){
  system(paste(matlabCommand, "'cd ../m; loadData; exit'"))
}
```

@@

## Data processing
Each individual EMG record was registered to the onset of platform motion and resampled.

>>>>

# if csv files do not exist, run matlab batch steps to populate them
if (!file.exists("../csv/c.csv")|!file.exists("../csv/m.csv")){
  system(paste(matlabCommand, "'cd ../m; loadData; exit'"))
}
```

@@

## Data processing
Each individual EMG record was registered to the onset of platform motion and resampled to a common timebase
